---
pagetitle: Rmd report
output:
  html_document:
    highlight: zenburn
    theme: cosmo
    df_print: paged
    toc: yes
    code_folding: hide
    code_download: true
---

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,

  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## make all required libraries available by loading radiant package if needed
if (is.null(shiny::getDefaultReactiveDomain())) library(radiant)

## include code to load the data you require
## for interactive use attach the r_data environment
# attach(r_data)
```

<style>
.btn, .form-control, pre, code, pre code {
  border-radius: 4px;
}
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
code, pre, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
}
code {
  color: #c7254e;
  background-color: #f9f2f4;
}
pre {
  background-color: #ffffff;
}
</style>

## Assignment 9 - Peter Cuomo

# Question 1

* R-squared for this model is **.33**
* For every unit increase in Price there is a -78.607 decrease in Demand. 

```{r}
result <- regress(
  CodfishStand, 
  rvar = "Demand", 
  evar = "Price"
)
summary(result)
```
# Question 2 


**Response variable: Demand_ln** 

**Explanatory variables: Price** 

* R squared decreased to **.177**
```{r fig.width = 7, fig.height = 8.08, dpi = 144}
result <- regress(
  CodfishStand, 
  rvar = "Demand_ln", 
  evar = "Price"
)
summary(result)

```
**Response variable: Demand_ln** 

**Explanatory variables: Price_ln** 

* R squared decreased to **.173**

```{r}
result <- regress(
  CodfishStand, 
  rvar = "Demand_ln", 
  evar = "Price_ln"
)
summary(result)
```

**Response variable: Demand** 

**Explanatory variables: Price_ln**

* R squared decreased to **.328**
```{r}
result <- regress(
  CodfishStand, 
  rvar = "Demand", 
  evar = "Price_ln"
)
summary(result)
```
# Question 3

* Prediction = **576.582**

  Standard Error = 287.274/1.967
  
  
* Standard Error = **146.047**.


```{r}
result <- regress(
  CodfishStand, 
  rvar = "Demand", 
  evar = "Price"
)
summary(result)
pred <- predict(result, pred_data = CodfishStand, pred_cmd = "Price=7.50", interval = "prediction")
print(pred, n = 10)
CodfishStand <- store(CodfishStand, pred, name = "pred_reg")
```

# Question 4 

* The mean predicted profit is **$1,361.5**
* The mean predicted outofstock probability is **.702**

```{r}
simdat <- simulater(
  const = c("Cost 4.5", "Sale 7.5", "Unsold 2.50", "q 500"), 
  norm = "D 576.582 146.047", 
  form = c(
    "prof=-Cost*q+Sale*ifelse(D>q,q,D)+Unsold*ifelse(D>q,0,q-D)", 
    "outofstock=ifelse(D>q,1,0)"
  ), 
  seed = 1234, 
  nr = 100000
)
summary(simdat, dec = 4)
register("simdat")
```

# Question 5 

* Optimal q is  **614** 
* The estimated out of stock probability for q of 614 is **.40**
* The mean outofstock for this gridsearch is .3550

```{r}
repdat <- repeater(
  simdat, 
  vars = "q", 
  grid = "q 350 1000 1", 
  sum_vars = c("q", "prof", "outofstock"), 
  byvar = "rep", 
  fun = "mean", 
  seed = 1234
)
summary(repdat, dec = 4)
register("repdat")
```
# Question 6 

* For both March 2nd and March 3rd the demand mean and standard error would be: **576.582 and 146.047**

```{r}
result <- regress(
  CodfishStand, 
  rvar = "Demand", 
  evar = "Price"
)
summary(result)
pred <- predict(result, pred_data = CodfishStand, pred_cmd = "Price=7.50")
print(pred, n = 10)
CodfishStand <- store(CodfishStand, pred, name = "pred_reg")
```
# Question 7 

* The expected profit is **4,376.0561**
* The outofstock probability is **.8192**

```{r}
simdat <- simulater(
  const = c("Cost 4.5", "Sale 7.5", "Unsold 2.50", "q 1500"), 
  norm = c("D1 576.582 146.047", "D2 576.582 146.047", "D3 576.582 146.047"), 
  form = c(
    "prof=-Cost*q+Sale*ifelse(D1+D2+D3>q,q,D1+D2+D3)+Unsold*ifelse(D1+D2+D3>q,0,q-(D1+D2+D3))", 
    "outofstock=ifelse(D1+D2+D3>q,1,0)"
  ), 
  seed = 1234, 
  nr = 100000
)
summary(simdat, dec = 4)
register("simdat")
```
# Question 8 

* The optimal q for this scenario would be **1,795**
* The estimate outofstock percentage for q of 1,795 is .40
* The mean outofstock for this gridsearch is 0.6065

```{r}
repdat <- repeater(
  simdat, 
  vars = "q", 
  grid = "q 1000 2200 1", 
  sum_vars = c("q", "prof", "outofstock"), 
  byvar = "rep", 
  fun = "mean", 
  seed = 1234
)
summary(repdat, dec = 4)
register("repdat")
```

